Submission

### 2021-05-10 code/Submission.Rmd
created tables with captions
supressed text output on likert

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(foreign)      
library(ggplot2)      
library(colorspace)   #better colors for ggplot
library(tidyverse)    
library(dplyr)
library(gridExtra)
library(viridis)
library(ggridges)
library(broom)
library(stargazer)
library(corrr)
library(GGally)
library(RColorBrewer)
library(grid)
library(likert) # for creating a likert plot
echoval <- F
load("../../Pew/pewTech.RData")
```

@@

```{r FACE3, echo= echoval, warning = F}
###Data Manipulation###
## Create df of FACE3
df_f3 <- pew %>% filter(FACE3a_W49 != "No Answer" & FACE3b_W49 != "No Answer" & FACE3c_W49 != "No Answer") %>% filter(FACE3a_W49 != "Refused" & FACE3b_W49 != "Refused" & FACE3c_W49 != "Refused") %>%  dplyr::select(c(FACE3a_W49, FACE3b_W49, FACE3c_W49, groupKnow))

@@

**Summary Statistics** 
```{r KF2-tables, echo=echoval}
KF2_T1 <- summary(likert(df_f3.reverse[,c(1:3)], grouping = df_f3.reverse[,4]))
knitr::kable(KF2_T1, "simple", caption = "Summary Statistics of Key Figure 2")
```

@@

```{r FACE3 Alt, echo=echoval, warning = F}
## 100% BarPlot
plot(likert(df_f3[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = FALSE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(foreign)      
library(ggplot2)      
library(colorspace)   #better colors for ggplot
library(tidyverse)    
library(dplyr)
library(gridExtra)
library(viridis)
library(ggridges)
library(broom)
library(stargazer)
library(corrr)
library(GGally)
library(RColorBrewer)
library(grid)
library(likert) # for creating a likert plot
library(kableExtra) # not needed but makes the table nicer
echoval <- F
load("../../Pew/pewTech.RData")
```

@@

```{r FACE3, echo= echoval, message=FALSE}
#TODO: deal with POS fig.cap = "Key Figure 2", fig.pos = "!H"
###Data Manipulation###
## Create df of FACE3
df_f3 <- pew %>% filter(FACE3a_W49 != "No Answer" & FACE3b_W49 != "No Answer" & FACE3c_W49 != "No Answer") %>% filter(FACE3a_W49 != "Refused" & FACE3b_W49 != "Refused" & FACE3c_W49 != "Refused") %>%  dplyr::select(c(FACE3a_W49, FACE3b_W49, FACE3c_W49, groupKnow))

@@

```{r KF2-tables, echo=echoval}
KF2_T1 <- summary(likert(df_f3.reverse[,c(1:3)], grouping = df_f3.reverse[,4]))
KF2_T1 <- KF2_T1[, c(1,2,3,5,6,7)] # remove neutral column b/c it isn't relevant
knitr::kable(KF2_T1, "simple", caption = "Summary Statistics of Key Figure 2")
```

@@

```{r FACE3 Alt, echo=echoval, message=FALSE}
## 100% BarPlot
plot(likert(df_f3[,c(1:3)], grouping = df_f3.reverse[,4]), legend.position="right", centered = FALSE, plot.percents=TRUE, plot.percent.low=FALSE, plot.percent.high=FALSE, plot.percent.neutral=FALSE, center = 2.5) + 
  scale_fill_manual(values = brewer.pal(n=4,"RdBu"), breaks = c("Not at all", "Not too much", "Somewhat", "A great deal")) + #order and color the likert boxes
  ggtitle(title2) +
  labs(caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy")+
  guides(fill = guide_legend(title="Responses", reverse = TRUE)) #to reverse the order in the legend
```
